\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}

\geometry{margin=1in}
\setstretch{1.2}

\begin{document}

\begin{center}
\textbf{\Large Probability Models for Discrete Randomized Outcomes}

\vspace{0.3cm}

\textbf{Ayman Azad} \\
Student ID: 202056081 \\
MATH--3030: Mathematical Inquiry \\
Project 1
\end{center}

\vspace{0.5cm}

\section*{Research Questions}

\begin{itemize}
    \item How are outcomes formally modeled using probability theory?
    \item How can expected value and variance be derived using this model?
    \item How does the outcome behave in the long run?
    \item Is there a similarity between Monte Carlo simulation results and the theoretical outcomes?
    \item How can regression models be used to make the outcome more predictable?
\end{itemize}

\section*{Methodology}

A discrete probability outcome will be constructed and analyzed using standard results from probability theory. Expected values and variances will be computed explicitly. Monte Carlo simulations will be used to compare numerical results with theoretical expectations. The convergence behavior of the model outcomes will be studied and analyzed. Additionally, regression models will be explored to examine how outcomes can be made more predictable.

\section*{Repository Link}

\noindent
\faGithub\ \href{https://github.com/aymanazad600/Project_1_Probability-model-for-discrete-randomized-outcome}{GitHub Repository}

\end{document}
